## Outline
- Total Inheritance in 2064
- Difference of Total Inheritance in 2064 between patterns
- Net Income in 2064
- Difference of Income in 2064 between patterns
- Inheritance and Income in 2064
- Difference of Inheritance and Income in 2064 between patterns
- Inheritance by year
- Difference of Inheritance by year
- Net Income by year
- Difference of Net Income by year


## Summary(1/3): Inheritance
```{r,  results = "asis", echo = FALSE, comment = NA, warning=FALSE,error=FALSE, message=FALSE}

kable(pivot_inh,caption="Inheritance")
```

## Summary(2/3): Net Asset
```{r,  results = "asis", echo = FALSE, comment = NA, warning=FALSE,error=FALSE, message=FALSE}
kable(pivot_last,caption="Net Asset")
```

## Summary(3/3): Income after donation
```{r,  results = "asis", echo = FALSE, comment = NA, warning=FALSE,error=FALSE, message=FALSE}
kable(pivot_net,caption="Income")
```

## Inheritance in 2064
```{r,  results = "asis", echo = FALSE, comment = NA, warning=FALSE,error=FALSE, message=FALSE}
plot(gg_inh_2064)
```

## Diff. of Inheritance
```{r,  results = "asis", echo = FALSE, comment = NA, warning=FALSE,error=FALSE, message=FALSE}
plot(gg_inh_2064_diff)
```

## Net Income in 2064
```{r,  results = "asis", echo = FALSE, comment = NA, warning=FALSE,error=FALSE, message=FALSE}
plot(gg_net_2064)
```

## Diff. of Net Income
```{r,  results = "asis", echo = FALSE, comment = NA, warning=FALSE,error=FALSE, message=FALSE}
plot(gg_net_2064_diff)
```

## Net Asset in 2064
```{r,  results = "asis", echo = FALSE, comment = NA, warning=FALSE,error=FALSE, message=FALSE}
plot(gg_last_2064)
```

## Diff. of Net Asset
```{r,  results = "asis", echo = FALSE, comment = NA, warning=FALSE,error=FALSE, message=FALSE}
plot(gg_last_2064_diff)
```

## Inheritance and Income in 2064
```{r,  results = "asis", echo = FALSE, comment = NA, warning=FALSE,error=FALSE, message=FALSE}
plot(gg_2064)
```

## Diff. Inheritance and Income in 2064
```{r,  results = "asis", echo = FALSE, comment = NA, warning=FALSE,error=FALSE, message=FALSE}
plot(gg_2064_diff)
```

## Inheritance and Asset in 2064
```{r,  results = "asis", echo = FALSE, comment = NA, warning=FALSE,error=FALSE, message=FALSE}
plot(gg_2064_b)
```

## Diff. Inheritance and Asset in 2064
```{r,  results = "asis", echo = FALSE, comment = NA, warning=FALSE,error=FALSE, message=FALSE}
plot(gg_2064_b_diff)
```


## Inheritance by year
```{r,  results = "asis", echo = FALSE, comment = NA, warning=FALSE,error=FALSE, message=FALSE}
plot(gg_inh)
```

## Difference of Inheritance by year
```{r,  results = "asis", echo = FALSE, comment = NA, warning=FALSE,error=FALSE, message=FALSE}
plot(gg_inh_diff)
```

## Net Income by year
```{r,  results = "asis", echo = FALSE, comment = NA, warning=FALSE,error=FALSE, message=FALSE}
plot(gg_net)
```

## Difference of Net Income by year
```{r,  results = "asis", echo = FALSE, comment = NA, warning=FALSE,error=FALSE, message=FALSE}
plot(gg_net_diff)
```

## Net Asset by year
```{r,  results = "asis", echo = FALSE, comment = NA, warning=FALSE,error=FALSE, message=FALSE}
plot(gg_last)
```

## Difference of Net Asset by year
```{r,  results = "asis", echo = FALSE, comment = NA, warning=FALSE,error=FALSE, message=FALSE}
plot(gg_last_diff)
```